---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbloldataR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `cbloldataR` is to provide a set of functions aimed for harvesting data of CBLOL from [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends), helping analysts, journalists, or enthusiasts to work with and visualize the tournament stats within R.  

## Installation

`cbloldataR` was created as an exercise for practising web scrapping and package devolopement and is not likely to be submitted to CRAN. You can install the latest development version from [GitHub](https://github.com/) with:

```{undefined eval=FALSE}
# install.packages("devtools")
devtools::install_github("pedrodrocha/cbloldataR")
```


## Load

```{r include=FALSE}
library(tidyverse)
```


```{r example}
library(cbloldataR)

```

## Use

The package offer access to eight tables of tidy data that you can harvest from [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends). 

1) `getData_editions()`: creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on each CBLOL edition. 

```{r editions}
editions <- getData_editions()
glimpse(editions)
```

2) `getData_titlesOrg()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL tournament wins per Organization.

```{r titlesOrg}
titlesOrg <- getData_titlesOrg()
glimpse(titlesOrg)
```


3) `getData_titlesPlayer()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL tournament wins per player
```{r titlesPlayer}
titlesPlayer <- getData_titlesPlayer()
glimpse(titlesPlayer)
```


4) `getData_rosters()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL rosters on each edition

```{r rosters}
rosters <- getData_rosters(Team = "paiN Gaming", Role = "Support")

rosters %>% 
  slice(1:10)

```

5) `getData_games()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL official games.


```{r games1}
# You can specify the Year and Split...
games1 <- getData_games(Year = 2020, Split = c("Split_1","Split_1_Playoffs"))
glimpse(games1)

```


```{r games2}
# ...and also the Org.
games2 <- getData_games(Team = "INTZ", Year = 2020, Split = c("Split_2"))
glimpse(games2)
```




[...]

### Notes

If you use the data always remember to attribute the source to [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends). 

If you encounter a clear bug, please file a minimal reproducible example on [GitHub](https://github.com/pedrodrocha/cbloldataR/issues).

