---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbloldataR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `cbloldataR` is to provide a set of functions aimed for harvesting data of CBLOL from [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends), helping analysts, journalists, or enthusiasts to work with and visualize the tournament stats within R.  

## Installation

`cbloldataR` was created as an exercise for practising web scrapping and package devolopement and is not likely to be submitted to CRAN. You can install the latest development version from [GitHub](https://github.com/) with:

```{undefined eval=FALSE}
# install.packages("devtools")
devtools::install_github("pedrodrocha/cbloldataR")
```


## Load

```{r include=FALSE}
library(tidyverse)
library(magrittr)
devtools::load_all()
```


```{r example, eval=FALSE}
library(cbloldataR)

```

## Use

The package offer access to tidy tables of data that you can harvest from [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends). 

**1)** `getData_editions()`: creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on each CBLOL edition. 

```{r editions}
editions <- getData_editions(Split = c("Split 1", "Split 2", "Split 1 Playoffs","Split 2 Playoffs"), Year = c(2015:2020))
glimpse(editions)
```

**2)** `getData_titlesOrg()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL tournament wins per Organization.

```{r titlesOrg}
titlesOrg <- getData_titlesOrg()
glimpse(titlesOrg)
```


**3)** `getData_titlesPlayer()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL tournament wins per player.

```{r titlesPlayer}
titlesPlayer <- getData_titlesPlayer()
glimpse(titlesPlayer)
```


**4)** `getData_rosters()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL rosters on each edition.

```{r rosters}

rosters <- getData_rosters(Year = c(2015:2020),Team = "INTZ",Role = "Support", Split = c("Split 1","Split 2"))

glimpse(rosters)

```

**5)** `getData_games()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on CBLOL official games.


```{r games1}

games <- getData_games(Year = 2020, Split = c("Split 2","Split 2 Playoffs"))
glimpse(games)

```


**6)** `getData_champion()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data on champions played in CBLOL official games.

```{r champion}
champion <- getData_champion(Role = "Mid",
                             Year = 2020, 
                             Split = c("Split 2","Split 2 Playoffs"))
glimpse(champion)
```


**7)** `getData_players()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data of players in CBLOL official games.
```{r, players}
players <- getData_players(Role = "Jungle", 
                           Year = 2020, 
                           Split = c("Split 2","Split 2 Playoffs"))

glimpse(players)
```


**8)** `getData_playersChampion()`: Creates a tibble containing [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends) data of players per Champion played in official games of CBLOL.

```{r players_champion}
players_champion <- getData_playersChampion(Role = "Jungle", 
                                            Year = 2020, 
                                            Split = c("Split 2",
                                                      "Split 2 Playoffs"))

glimpse(players_champion)

```


### Notes

If you use the data always remember to attribute the source to [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends). 

If you encounter a clear bug, please file a minimal reproducible example on [GitHub](https://github.com/pedrodrocha/cbloldataR/issues).

### Version Control

* Version: 0.0.0.9001 - 08.08.2020 - fixing issues with AD Carry entries in both `getData_players()` and `getData_playersChampion()`.
* Version: 0.0.0.9002 - 23.08.2020 - adding 2020/2 PlayOffs.
* Version: 0.0.0.9003 - 11.09.2020 - editing how arguments are written while calling the package functions.
* Version: 0.0.0.9004 - 16.10.2020 - improving tests and error handling
