---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbloldataR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `cbloldataR` is to provide a set of functions aimed for harvesting data of CBLOL from [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends), helping journalists, analysts or enthusiasts to work with and vizualize the tournament stats within R.  

## Installation

`cbloldataR` was created as an exercise for practising web scrapping and package devolopement and is not likely to be submitted to CRAN. You can install latest development version from [GitHub](https://github.com/) with:

```{undefined eval=FALSE}
# install.packages("devtools")
devtools::install_github("pedrodrocha/cbloldataR")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(cbloldataR)
## basic example code
```

### Notes

If you use the data always remember to attribute the source for [Leaguepedia](https://lol.gamepedia.com/Circuit_Brazilian_League_of_Legends). 

If you encounter a clear bug, please file a minimal reproducible example on [GitHub](https://github.com/pedrodrocha/cbloldataR/issues).

